MSF_Groupwork-NBA_shotlog

### 2016-10-12 MSFGroupwork-NBAHotHand.Rmd
more code-hot hand

###PLAYER 3 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter1 
set.seed(57)
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = length(streak_per_player[[3]]), replace = TRUE, prob = c(shooting_percentage[[3]], 1 - shooting_percentage[[3]]))
simul_shooter

>>>>

###PLAYER 3 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter1 
set.seed(57)
shot_results <- c('made', 'missed')javascript:;
simul_shooter <- sample(shot_results, size = length(streak_per_player[[3]]), replace = TRUE, prob = c(shooting_percentage[[3]], 1 - shooting_percentage[[3]]))
simul_shooter
